Target Markdown

### 2022-05-05 _targets.Rmd
add create_dfm()
targets

@@

# load libraries for targets notebook
library(targets)
library(tidyverse, quietly = TRUE)

@@

@@

# load libraries for make
tar_option_set(packages = c("tidyverse", "quanteda"))

@@

```{targets texts, tar_simple = TRUE}
read_csv2(here::here("data_core_pubs_trim.csv"))
```

# Text pre-processing

```{targets}
list(
    tar_target(corpus,
               extract_corpus(texts)),
    tar_target(tokens,
               process_tokens(corpus, texts))
)
```

# Check results

```{r}
tar_read(tokens)
```

>>>>

# Set up targets environment

Here we run necessary code for `targets` setup.

@@

# load libraries for targets notebook
library(targets)
library(dplyr, quietly = TRUE)

@@

# Dependencies

Here, we load packages and custom functions required in the pipeline.

@@

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm"
                            ))

@@

```{targets data_import}
list(

    tar_target(one_author,
               read.csv2(here::here("data", "raw", "Binter_pubs.csv")),
               format = "qs"),
    tar_target(two_authors, read.csv2(here::here("data", "raw", "Binter_Kvapilova_pubs.csv")),
               format = "qs")

)
```

# Coauthorship network

```{targets network}

list(

    tar_target(edgelist,
               make_edgelist(one_author),
                format = "qs"),
    tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE) )

)

```

# Topic model

```{targets topic_model}
list(

   tar_target(topic_model, 
              make_topic_model(two_authors),
               format = "qs")

)
```

# Researcher independence indicator (RII) part 1 - eigenvector centrality

```{targets RII1}

list(

    tar_target(eigen_centr,
               calc_eigen_centr(graph), 
               format = "qs")

)

```

# Researcher independence indicator (RII) part 2 - clustering coefficient

```{targets RII2}

list(

    tar_target(clustering,
               calc_clustering(graph), 
               format = "qs")

)

```

# Researcher independence indicator (RII) part 3 - independent publications

```{targets RII3}

list(

    tar_target(ind_pubs,
               calc_ind_pubs(one_author), 
               format = "qs")

)

```

# Researcher independence indicator (RII) part 4 - independent topics

```{targets RII4}

list(

    tar_target(ind_topics,
               calc_ind_topics(topic_model, two_authors), 
               format = "qs")

)

```

# Researcher independence indicator (RII) part 4 - independent topics: alternative way via cosine similarity

```{targets RII4_2}

list(

    tar_target(ind_topics_cs,
               calc_cos_sim(topic_model, two_authors), 
               format = "qs")

)

```

# Final indicator

```{r}

```
# Article

```{targets article}
list(
    tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
)

```
